---
title: "sankey_vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{sankey_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


# Introduction: This vignette explains how to use the `ymsankey` package to create Sankey plots for visualizing the contribution of various risk factors to stroke.


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Example

```{r setup, include=FALSE}
library(ymsankey)
library(ggplot2)

```

# Define colors
colors <- c("Hypertension" = "#94B992", 
            "Diabetes" = "#CA6C56", 
            "Smoking" = "#87AAC2", 
            "Hypercholesterolemia" = "#CD925F", 
            "Obesity" = "#546C91")

# Load the data
load("/Users/yakoutmezgueldi/Desktop/Jobs/Cedars Sinai Job Lab/Assignment No 2/sankey_data.RData") #Replace with the actual path to your data file

# Create version 1 of the plot
plot1 <- sankey_plot(data_melt, colors, version = 1)
print(plot1)

# Create version 2 of the plot
plot2 <- sankey_plot(data_melt, colors, version = 2)
print(plot2)

install.packages("devtools")
library(devtools)
devtools::document(R/data.R)



